Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-10 automatica/paper.tex
revised contributions to address comment

  % Additions from CAV:
  % continuous time
  % floating point 
\item We automatically generate \emph{correct-by-construction} digital
  controllers using an inductive synthesis approach (CEGIS).  
  This application is non-trivial and addresses challenges specific to digital control
  systems, such as the presence of A/D quantizers and FWL operations.  %% In particular, we
  %% have found that a two-stage verification engine that continuously refines
  %% the precision of the fixed-point representation of the plant yields a
  %% speed-up of two orders of magnitude over a conventional one-stage
  %% verification engine.
%
  %\item  We compute
  The automatically computed state-feedback controllers 
  guarantee a given safety specification alongside a stability property. 
  \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
  function representations, which are inadequate to prove safety requirements. } 
%
\item We provide two novel algorithms: the first, a na\"ive approach, relies on 
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction/refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of 
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant. 
%
\item We develop a model for different sources of quantization error and account for 
  their effect on safety.  We give bounds that ensure the
  safety of our controllers in a hybrid (i.e., continuous/digital) domain.

>>>>

  % Additions from CAV:
  % continuous time
  % floating point 
\item We automatically generate \emph{correct-by-construction} digital
  controllers using an inductive synthesis approach (CEGIS).  
  %% This application is non-trivial and addresses challenges specific to digital control
  %% systems, such as the presence of A/D quantizers and FWL operations.  
  In addition a stability property, the automatically computed state-feedback
  controllers must also guarantee a given safety specification.
  The implication is that, as opposed to existing
  methods for controller synthesis which rely on transfer function
  representations, we must consider a state-space representation of
  the physical system. Such a representation requires ensuring the
  specification over actual traces of the model, alongside the
  numerical soundness required by the effects of discretisation and
  finite-precision errors.

%%   \note{[this statement is way too broad] Existing methods for controller synthesis rely on transfer 
%%   function representations, which are inadequate to prove safety requirements. } 
%% %
\item We provide two novel algorithms: the first, a na\"ive approach, relies on 
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction/refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of 
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant. 
%
\item We develop a model for different sources of quantization error and account for 
  their effect on safety.  We give bounds that ensure the
  safety of our controllers in a hybrid (i.e., continuous/digital) domain.
